---
title: "Week 01 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

1.  Explain coercion rules. Create an example that demonstrates the fixed order of the coercion rules.
#You can force one type to be another and a specific pattern to perform.
logicals -> integers -> doubles -> character

```{r}
team1_numbers <- c(5, 10, 15, 20)
team2_numbers <- c(2, 4, 6, 8)
```
```{r}
typeof(team1_numbers)

is.double(team1_numbers)
is.integer(team1_numbers)
is.numeric(team1_numbers)
```
```{r}
team1_numbers <- as.integer(team1_numbers)

is.double(team1_numbers)
is.integer(team1_numbers)
is.numeric(team1_numbers)
```
2.  The following code will generate a warning. Explain why.
#the as.integer should be an is.integer because the as.integer is forcing it to become an integer when it is logicals. the is.integer states what it actually is.
```{r}
as.integer(c("one", "two", "three"))
```
```{r}
is.integer(c("one", "two", "three"))
```


3.  Create a vector of a sequence of integers starting at 2, ending at 100, and increasing by 2. Assign the vector to an object called `evens`. Coerce the vector to be of type `integer`. Confirm that the vector is of type `integer`.

```{r}
seq(2, 100, by=2)
```
```{r}
evens <- seq(2, 100, by=2)
```
```{r}
evens
```
```{r}
as.integer(evens)
```
```{r}
is.integer(evens)
```
4.  Create a vector of random numbers with a length equal to your vector in exercise 3. Use a seed with a value of 730 before creating your vector. Assign the vector to an object called `randoms`. Confirm the type of the vector.

```{r}
set.seed(730)
runif(50, 2, 100)
```

```{r}
randoms <- runif(50, 2, 100)
```
```{r}
typeof(randoms)
```
5.  Create a vector demonstrating which values in exercise 3 are greater than `0.75`. Assign the vector to an object called `logicals`. Confirm the type of the vector.

```{r}
runif(evens) >0.75
```

```{r}
logicals <- runif(evens) >0.75
```
```{r}
typeof(logicals)
```
6.  Create a data frame including the three vectors created in exercises 3 through 5. Assign it to an object following best practices for naming.

```{r}
data.frame(randoms, evens, randoms_evens = 1:50)
```
```{r}
all_teams_numbers <- data.frame(randoms, evens, randoms_evens = 1:50)
```
```{r}
all_teams_numbers
```

7.  Create a new object which is the sum of `evens` and `randoms` all divided by 3. Demonstrate how to calculate basic summary statistics for this new object (mean, median, minimum, maximum, standard deviation, variance).

```{r}
(evens + randoms)/3
```
```{r}
all_evens_randoms <- (evens + randoms)/3
```
```{r}
all_evens_randoms
```
```{r}
mean(all_evens_randoms)
median(all_evens_randoms)
min(all_evens_randoms)
max(all_evens_randoms)
sd(all_evens_randoms)
var(all_evens_randoms)
```
8.  We discussed the idea that R is a "vectorized" language. Explain this concept. Why is it important?
      #long list of numbers and characters are all vectors. all help standardize the structure of the data such as atomic vectors(logical, numeric, character).
9.  Run the `sessionInfo` function in a chunk.

```{r}
sessionInfo
```
